---
title: "Data Processing"
author: "Adéla Sobotkova & Rebecca Folmer Schade"
date: "13 okt 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction 
In this script, data collected on mounds in the Yambol region is processed and converted from a spatial object (shapefile) supported by the **sf** package into a dataframe in the csv format. 

```{r, echo = FALSE}
# Loading packages
library(tidyverse)
library(sf)
```


## Loading the dataset
The dataset is loaded, and filtered into another dataset based on a conservative estimate of which of the collected datapoints indicate burial mounds.  

```{r data}
# Loading in the master_sp from shapefile enriched_all.shp
master_sp <- st_read("../data/enriched_all.shp")
summary(master_sp)

# Creating a conservative dataset
conservative_sp <- master_sp %>% filter(Type == "Burial Mound" | Type == "Extinct Burial Mound") 

# Turning the spatial object into a tibble
tble_mounds <- as.tibble(st_drop_geometry(conservative_sp))
class(tble_mounds)

# the variable HeghtMx (mound height) bahaves strangely as an artifact of loading the spatial object
# This is a quick-fix for that problem
tble_mounds$HeghtMx <- tble_mounds$HeghtMx %>% as.character() %>% as.numeric()
```

## Fixing landuse 

Lets review the most common categories of landuse AROUND mounds

```{r}
tble_mounds %>%
  filter(Type == "Burial Mound" | Type == "Extinct Burial Mound") %>%   group_by(LU_Arnd) %>% 
  tally() %>% 
  mutate(perc = round(n/sum(n)*100, 2)) %>% 
  arrange(desc(n)) %>% 
  as.matrix() %>% 
  print()
```
Annual agriculture, pasture and scrub are the most common categories, with forest perhaps the last meaningful category. Perennial agriculture, other and urban might be best merged into Other, or perennial with agriculture and the rest in Other. 

It might be a good idea to merge the small categories into larger ones, especially where is similar relationship (Annual and Perennial, Urban and Other)
```{r}
# > Re-leveling the factor to merge categories
# reviewing the variable
levels(tble_mounds$LU_Arnd) # How many levels are there?
tble_mounds$LU_Arnd[1:10] # Having a look at the variable

# Creating a list of new labels/levels (in order)
new_levels <- c("Agriculture", "Forest", "Other", "Pasture", "Agriculture", "Scrub", "Other")
levels(tble_mounds$LU_Arnd) <- new_levels # Re-naming the levels
tble_mounds$LU_Arnd[1:10] # Testing if it worked
```

## Creating 'Robbed' column
To take whether or not a mound hs been robbed into account in later analysis. 

```{r}
tble_mounds <- tble_mounds %>%
  mutate(Robbed = str_extract(PrncSOI, "Loot")) %>%
  mutate(Robbed = case_when(is.na(Robbed) ~ "No",
                            Robbed == "Loot" ~ "Yes"))
```

## Adding distances to town and Bulgarian border in kms
if it is easier for the logit output...

```{r}
tble_mounds$distBGkm <- tble_mounds$distBG/1000 
tble_mounds$distTownkm <- tble_mounds$distTwn/1000 
```

## Clarifying condition
We need to streamline a bit the Condition variable, clarifying NAs and recoding number 6 as it should be 1-5 Likert scale. Beware that this code will clear uncertainty such as 3? or 2? , where condition was hard to gauge in the field.

```{r}
# Having a look at the recorded data 
levels(factor(tble_mounds$Conditn))

# simplifying the variable
tble_mounds <- tble_mounds %>%
  mutate(Condition = as.character(str_extract(Conditn, "\\d"))) %>%
  mutate(Condition = case_when(Condition == 0 ~ "NA",
                               Condition == 6 ~ "5",
                               Condition != 0 ~ Condition))

tble_mounds$Condition <- as.factor(tble_mounds$Condition)
unique(tble_mounds$Condition)
```

## Subsetting the dataset
Only the variables relevant in later analysis are kept.

```{r}
# Selecting columns
analysis_tble <- tble_mounds %>% dplyr::select(TRAP, 
                                               Type, 
                                               LU_Arnd, 
                                               HeghtMx, 
                                               distBG, 
                                               distTwn, 
                                               Robbed, 
                                               distTownkm, 
                                               distBGkm, 
                                               Condition)

# Re-nameing columns
new_colnames <- c("TRAP", "Type", "LU_Around", "Height_Mx", "Dist_BG", "Dist_Town", "Robbed", "Dist_Town_KM", "Dist_GB_KM", "Condition")
colnames(analysis_tble) <- new_colnames
```

## Writing a csv with the result

```{r}
write_csv(analysis_tble, "../data/analysis_data.csv")
```
