---
title: "Simulation"
author: "Rebecca Folmer Schade"
date: "16 jun 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "..")
```

### Loading packages

```{r}
pacman::p_load(pacman, tidyverse)
```

### Loading data 

```{r}
# Loading the "modified_vulnerability" dataset
mounds <- read_csv("data/modified_vulnerability.csv")

# Removing NAs 
variables <- c("LU_Arnd", "Robbed", "HeghtMx", "distTownkm", "distBGkm")
mounds <- mounds %>% drop_na(any_of(variables))
```

## Simulations
The data will be simulated to match five(?) different situations:    

1. A conversion of all forest to agriculture
2. A conversion of all forest to pasture
3. A conversion of all pasture to annual agriculture
4. An increase in distance of one standard deviation from the nearest edge of a city, town, or village
5. An increase in distance of one standard deviation from the Bulgarian border

### Forest to agriculture 

```{r}
#=====> Simulating data 
simulation_1 <- mounds

# Re-leveling the factor to convert categories
simulation_1$LU_Arnd <- as.factor(simulation_1$LU_Arnd)
levels(simulation_1$LU_Arnd) # How many levels are there?
# > The "Perennial" category covers both perennial and annual agriculture, "Urban" covers both urban and others

simulation_1$LU_Arnd[1:10] # Having a look at the variable
new_levels_1<- c("Agriculture", "Pasture", "Agriculture", "Scrub", "Other") # Making a list of new levels (in order)
levels(simulation_1$LU_Arnd) <- new_levels_1 # Re-naming the levels
simulation_1$LU_Arnd[1:10] # Testing if it worked
```

### Forest to pasture

```{r}
#=====> Simulating data 
simulation_2 <- mounds

# Re-leveling the factor to convert categories
simulation_2$LU_Arnd <- as.factor(simulation_2$LU_Arnd)
levels(simulation_2$LU_Arnd) # How many levels are there?

simulation_2$LU_Arnd[1:10] # Having a look at the variable
new_levels_2<- c("Pasture", "Pasture", "Perennial", "Scrub", "Urban") # Making a list of new levels (in order)
levels(simulation_2$LU_Arnd) <- new_levels_2 # Re-naming the levels
simulation_2$LU_Arnd[1:10] # Testing if it worked
```

### Pasture to annual agriculture

```{r}
#=====> Simulating data 
simulation_3 <- mounds

# Re-leveling the factor to convert categories
simulation_3$LU_Arnd <- as.factor(simulation_3$LU_Arnd)
levels(simulation_3$LU_Arnd) # How many levels are there?

simulation_3$LU_Arnd[1:10] # Having a look at the variable
new_levels_3 <- c("Forest", "Perennial", "Perennial", "Scrub", "Urban") # Making a list of new levels (in order)
levels(simulation_3$LU_Arnd) <- new_levels_3 # Re-naming the levels
simulation_3$LU_Arnd[1:10] # Testing if it worked
```

###  Increase in distance from the nearest edge of a city, town, or village

```{r}
#=====> Simulating data 
simulation_4 <- mounds

# Calculating the standard deviation and adding it to the distTownkm variable. 
simulation_4$distTownkm <- simulation_4$distTownkm + sd(simulation_4$distTownkm)
```

###  Increase in distance from the nearest edge of a ciry, town, or village

```{r}
#=====> Simulating data 
simulation_5 <- mounds

# Calculating the standard deviation and adding it to the distTownkm variable. 
simulation_5$distBGkm <- simulation_5$distBGkm + sd(simulation_5$distBGkm)
```


